MP MetaAnalysis

### 2018-11-14 Paper_Analyses.Rmd

We identified several variables to assess the influence of data analysis choices. These variables fall into two types of categories: time-related and dependent variable related. In the following analyses, we discuss the theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these choices have on mispronunciation sensitivity development.

@@

When designing mispronunciation sensitivity studies, experimenters choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. Across papers, trial length varied from `r with(trial_length_info, min(trial_length))*1000` to `r with(trial_length_info, max(trial_length))*1000` ms, with a mode of `r with(dat, getmode(trial_length))*1000` ms. There was an inverse relationship between infant age and trial length, such that younger infants were given trials of a longer length, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`). Presumably, younger infants may be given longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).

Unlike the length of trial, the length of the post-naming phase analyzed can be chosen after the experimental data is collected. Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`, while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`. Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a mode of `r with(dat, getmode(post_nam_dur))*1000` ms. Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants were analyzed using a longer length of post-naming phase, although here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`). Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998). Furthermore, the proportion of post-naming phase time window analyzed in comprison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`). Although trial length did not differ by infant age, the size of the post-naming phase time window analyzed did differ by infant age.

When analyzing eye-movements, it is important to consider the amount of time it takes for an eye movement to be initiated in response to a stimulus. Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991). In mispronunciation sensitivity studies, however, this has often been extended to 367 ms (e.g. Swingley & Aslin, 2000, 2002, 2007). Across papers, the majority used a similar offset value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions. We note that Swingley (2009) also included offset values of 1133 ms to analyze responses to coda mispronunciations. There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, *p* `r psig(offset.l$p.value)`). This lack of a relationship is perhaps driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.

Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and are therefore susceptible to a higher rate of false-positives. Considering that differences in these choice were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming phase time window or the offset time influenced sensitivity to mispronunciations.

### Length of post time

@@

We first assessed whether size of post-naming phase analyzed had an impact on the size of mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming phase size as a moderator. The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`. This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the size of the post-naming phase analyzed. We next assessed whether post-naming phase size was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`. The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`. This relationship is plotted in Figure 3a. The results suggest that although the size of the post-naming phase analyzed did not impact infants' likelihood to fixate the target upon hearing the mispronunciation, it did significantly impact mispronunciation sensitivity. Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.

Considering that we also found a relationship between the length of the post-naming phase analyzed and infant age, such that younger ages had a longer post-naming phase time window of analysis, we next examined whether the size of post-naming phase analyzed modulated the development of mispronunciation sensitivity. For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`. This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed. We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`. The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`. This relationship is plotted in Figure 3b. Smaller post-naming phase size lead to greater increases in mispronunciation sensitivity with development. For example, experimental conditions analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas a post-naming phase of greater than 2000 ms leads to either no impact of age on mispronunciation sensitivity or a negative relationship between age and mispronunciation sensitivity.

@@

### Length of offset time

@@

We next assessed whether offset time had an impact on the size of mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including offset time as a moderator. The moderator test was not significant `r mod_test(rma_offset)` and the estimate for offset time was very small, $\beta$`r full_estimate(rma_offset_eff)`. This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the offset time used to analyze the data. We next assessed whether offset time was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was very small and not significant $\beta$`r full_estimate(rma_offset_MS_eff)`.

@@

Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words. Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the baseline. The purpose of the baseline is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to cup) which may drive PTL scores in the post-naming phase. As described in the Data Analysis sub-section of the Methods, there was considerable variation across papers in way that baseline was calculated, resulting in different measured outcomes or dependent variables. Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase. This results in one value, which is then compared with a chance value of 0. When positive, this indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced) relative to the pre-naming baseline PTL. We will refer to this dependent variable as the Difference Score. Another dependent variable, which was used in `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions, directly compared compared the post- and pre-naming PTL scores with one another. This requires two values, one for the pre-naming phase and one for the post-naming phase. A greater post compared to pre-naming phase PTL indicates that increased their target looks after hearing the naming label. We will refer to this dependent variable as Pre vs. Post. Finally, the remaining `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions compared the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures. We will refer to this dependent variable as Post.

The Difference Score and Pre vs. Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences. The Post dependent variable, in contrast, does not consider pre-naming preferences. To our knowledge, there is no theory or evidence to drive choice of dependent variable, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis. We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations. Considering that the dependent variable Post differs in its consideration of pre-naming preferences, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs. Post dependent variables.

@@

We next examined whether the type of dependent variable calculated modulated the development of mispronunciation sensitivity. For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was significant `r mod_test(rma_post_dur_AGE)`, but the estimates for the interaction between Pre vs. Post and age ($\beta$`r full_estimate(rma_within_AGE_effprepost)`) as well as Difference Score and age ($\beta$`r full_estimate(rma_within_AGE_effdiff)`) were not different from that of the Post dependent variable. This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or type of dependent variable. We next assessed whether the relationship between dependent variable and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant `r mod_test(rma_within_AGE_MS)`. The estimate for the interaction between Pre vs. Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`). This relationship is plotted in Figure 4b. When the dependent variable was Pre vs. Post, mispronunciation sensitivity decreased with infant development, while in comparison, when the dependent variable was Post, mispronunciation sensitivity increased with infant development. There was no difference in mispronunciation sensitivity change with infant development between the Post and Difference Score dependent variables.

@@

## Controlling for researcher choice

>>>>

[Christina] This section talked about several variables in 2 categories, but in reality there are only 2 variables, right? I am not 100% sure about total trial length as being the first or being mentioned at all, might it be better to focus on time window analyzed and then say "Oh, btw, total trial length totally does nothing so we don't have to discuss it further" I am not sure, so feel free to re-rewrite this, but now it better lines up with everything before because trial length kinda comes out of nowhere.

We identified two sets of variables which varied across papers to assess the influence of data analysis choices on resulting effect size: the time course of a trial and time window analyzed and which dependent variable(s) were reported. In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices have on mispronunciation sensitivity development.

@@

[Christina] Ideally load all libraries in the beginning of the doc. (reshape)

[Christina] Is there a reason you choose mode and not median?

[Christina] Would it make sense to present dependent variable first?

[Christina] So if you go with my suggestion from above, I would just add this sentence at the beginning of the next paragraph: "Before we focus on analysis choice relating to time windows, we must first discuss overall trial length, because it limits the overall time window available to analyze and might thus predict which time window was analyzed."

When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. Across papers, trial length varied from `r with(trial_length_info, min(trial_length))*1000` to `r with(trial_length_info, max(trial_length))*1000` ms, with a mode of `r with(dat, getmode(trial_length))*1000` ms. There was an inverse relationship between infant age and trial length, such that younger infants were presented with longer trials, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`). Presumably, younger infants may be exposed to longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).

Unlike the length of trial, the length of the post-naming phase analyzed can be chosen after the experimental data is collected. Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`). Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a mode of `r with(dat, getmode(post_nam_dur))*1000` ms. Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants'looking times were analyzed using a longer post-naming phase, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`). Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).

[Christina] I think the proportion needs more explanation, also because later we have proportions of looks to target.

Furthermore, the proportion of post-naming phase time window analyzed in comparison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`). To summarize, we observe variation in time-related aspects related to infants' age. This variation is most pronounced, and even significant, for the time window that is being analyzed after the target label has been heard.

[Christina] The canfield & haith paper is for visual stimuli, right? So add that before "stimulus". And then add to the next sentence that the longer latnecies are because ther eis addiitonal language processing required which EEg shows in adults to take X ms (400 for N400?).

[Christina] Can you add info how many papers did not report the analyzed variables? Across this whole section, I mean.

When analyzing eye-movements, it is important to consider the amount of time it takes for an eye movement to be initiated in response to a stimulus. Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991). In mispronunciation sensitivity studies, however, this has often been extended to 367 ms (e.g. Swingley & Aslin, 2000, 2002, 2007). Across papers, the majority used a similar offset value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions. We note that Swingley (2009) also included offset values of 1133 ms to analyze responses to coda mispronunciations. There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, *p* `r psig(offset.l$p.value)`). This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.

Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman, A., & Loken, E. (2013). The garden of forking paths: Why multiple comparisons can be a problem, even when there is no “fishing expedition” or “p-hacking” and the research hypothesis was posited ahead of time. Department of Statistics, Columbia University.). Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming time window or the offset time influenced sensitivity to mispronunciations.

### Length of post naming time window

@@

[Christina] I think it's a bit inconsistent whether it's post naming phase or window, how about window? Phase sounds wrong to me. or analysis window? I also find phase size odd, and again prefer window (window size). Your call though.

We first assessed whether size of post-naming phase analyzed had an impact on the size of the reported mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming window size as a moderator.

[Christina] the next bit is weird, in the pdf it's significant, but you write it's not. Also, I think the beta is quite large anbd the CI reasonably distinct from 0.

The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`.

[Christina] Even if a test is not significant, this next sentence is always wrong because we did not test whether it's the same (i.e. we did not do an equivalence or Bayesian test!)
This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the size of the post-naming phase analyzed. We next assessed whether post-naming phase size was related to mispronunciation sensitivity.

[Christina] To be sure, you base this again on the combined data and only plot differences for easier visualizations in figure 3? Ideally make that clear. Also, some suggestions to vary this sentence (also earlier in the paper)
"To investigate mispronunciation sensitivity, we considered data from both conditions in a joint analysis"
"Analyzing all data with condition (c, mp) as additional moderator leads to the following results"
etcetc

We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`. The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`. This relationship is plotted in Figure 3a. The results suggest that although the size of the post-naming phase analyzed did not impact infants' likelihood to fixate the target upon hearing the mispronunciation, it did significantly impact mispronunciation sensitivity. Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.

Considering that we also found a relationship between the length of the post-naming phase analyzed and infant age, such that younger ages had a longer post-naming phase time window of analysis, we next examined whether the size of post-naming phase analyzed modulated the development of mispronunciation sensitivity. For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`. This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed. We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`.

[Christina] lots of NAs here in the pdf

The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`. This relationship is plotted in Figure 3b. Smaller post-naming phase size lead to greater increases in mispronunciation sensitivity with development.

[Christina] The next sentence as weird, check whether my corrections make sense

For example, when experimental conditions were analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas there is no or a negative relation of mispronunciation sensitivity and age if the analyzed post-naming phase is greater than 2000 ms leads. In other words, all three possible hypotheses might be supported depending on analysis choices made.

[Christina] I think it's important to remind the reader here that this is our key question, namely how age and mp sensitivity are related.

@@

### Offset after target naming

@@

We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity. First, we calculated the meta-analytic effect size for object identification in response to mispronounced target words/images, including offset time as a moderator.

[Christina] again, the pdf tells me sth different

The moderator test was not significant `r mod_test(rma_offset)` and the estimate for offset time was very small, $\beta$`r full_estimate(rma_offset_eff)`.

[Christina] Again, we didn't test, so say sth like "did not differ significantly."

This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the offset time used to analyze the data. We next assessed whether offset time was related to mispronunciation sensitivity.

[Christina] Again, rewording suggestion: "When investigating mispronunciation sensitivity by including condition, the moderator test with was ...

We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`.

[Christina] Generally, it might be easier to kick out all object recognition analyses (what do they tell us?) and start out that we only analyze MP sensitivity, i.e. consider the whole dataset and always include condition as moderator.

@@

Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words. Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the baseline. The purpose of the baseline is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase. As described in the Data Analysis sub-section of the Methods, there was considerable variation across papers in way that baseline was calculated, resulting in different measured outcomes or dependent variables. Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase. This results in one value, which is then compared with a chance value of 0. When positive, this indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced) relative to the pre-naming baseline PTL. We will refer to this dependent variable as the Difference Score. Another dependent variable, which was used in `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions, directly compared the post- and pre-naming PTL scores with one another. This requires two values, one for the pre-naming phase and one for the post-naming phase. A greater post compared to pre-naming phase PTL indicates that increased their target looks after hearing the naming label. We will refer to this dependent variable as Pre vs. Post. Finally, the remaining `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions compared the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures. We will refer to this dependent variable as Post.

[Christina] Did I ask the following already: Do we know whether subtrations were on the trial level? Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.

The Difference Score and Pre vs. Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences. The Post dependent variable, in contrast, does not consider pre-naming preferences.

[Christina] Actually, in other domains (eeg, longitudinal studies, RCTs) people tlak a lot about whether or not to consider a baseline, so this is not strictly true.

To our knowledge, there is no theory or evidence to drive choice of dependent variable, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis. We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations. Considering that the dependent variable Post differs in its consideration of pre-naming preferences, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs. Post dependent variables.

@@

We next examined whether the type of dependent variable calculated modulated the development of mispronunciation sensitivity. For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was significant `r mod_test(rma_post_dur_AGE)`, but the estimates for the interaction between Pre vs. Post and age ($\beta$`r full_estimate(rma_within_AGE_effprepost)`) as well as Difference Score and age ($\beta$`r full_estimate(rma_within_AGE_effdiff)`) were not different from that of the Post dependent variable. This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or type of dependent variable. We next assessed whether the relationship between dependent variable and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant `r mod_test(rma_within_AGE_MS)`. The estimate for the interaction between Pre vs. Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`). This relationship is plotted in Figure 4b. When the dependent variable was Pre vs. Post, mispronunciation sensitivity decreased with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity increased with infant age. There was no difference in mispronunciation sensitivity change with infant development between the Post and Difference Score dependent variables.

@@

## Controlling for analysis choices
